Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-19 paper/paper.tex
Update exponential scores table

In order to address this issue, the Workflow-Aware DPDS (WA-DPDS) algorithm extends 
DPDS by introducing a workflow admission procedure. The admission procedure is
invoked whenever WA-DPDS sees the first task of a new workflow at the head of the 
priority queue (i.e. no other tasks from that workflow have been scheduled yet). 
The procedure estimates if there is enough
budget remaining to admit the new workflow: if not, all its tasks are rejected.
Algorithm~\ref{alg:wa-dpds} estimates the cost of admitting a new workflow and
compares it to the current cost (consumed budget) and remaining budget, taking
into account that started VMs have been already paid for. It adds a small safety
margin choosen to avoid overestimation of a budget.

@@

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & TOTAL\tabularnewline
\hline
DPDS      &   58 &  45 &  46 &  15  &  9 & 173\tabularnewline
WA-DPDS   &    90 &  96  & 84  & 29 &  17 & 316\tabularnewline
SPSS     &    48 &  27 & 173 &  75 &  42 & 365\tabularnewline
\end{tabular}
\medskip

>>>>

In order to address this issue, the Workflow-Aware DPDS (WA-DPDS) algorithm extends 
DPDS by introducing a workflow admission procedure. The admission procedure is
invoked whenever WA-DPDS sees the first task of a new workflow at the head of the 
priority queue (i.e. no other tasks from the new workflow have been scheduled yet). 
The admission procedure estimates if there is enough budget remaining to admit the 
new workflow: if not, all its tasks are rejected.
Algorithm~\ref{alg:wa-dpds} estimates the cost of admitting a new workflow and
compares it to the current cost (consumed budget) and remaining budget, taking
into account that started VMs have been already paid for. It adds a small safety
margin chosen to avoid overestimation of a budget.

@@

(c) Exponential score $s$:
\medskip
\begin{tabular}{r|cccccc}
 & M & C & L & E & S & TOTAL\tabularnewline
\hline
DPDS      &   58  & 45 &  19 &  14  &  0 & 136\tabularnewline
WA-DPDS   &    90  & 96  & 57  & 27 &   8 & 278\tabularnewline
SPSS     &    31 &  18 &  170  & 75 &  42 & 336\tabularnewline
\end{tabular}
\medskip
